Fast Bayesian Inference for Exoplanet Discovery in Radial Velocity Data

### 2014-12-26 Paper/ms.tex
Eccentricity prior

An apparently strange choice is the conditional prior for the orbital
periods, which is a biexponential distribution. A more conventional choice
would have been a normal distribution. However, the \citet{rjobject} software
needs to know the corresponding cumulative distribution and its inverse, which
are not available in closed form for the normal distribution.
The prior for the velocity semi-amplitudes $\{A_i\}$ is important and will affect the
inferred number of planets $N$. For example, if the prior allows for very
low amplitude planets to exist, the data will not rule this out, and the posterior
for $N$ will include the possibility of large numbers of planets. The prior
will influence how many of these low amplitude planets will exist: if we
believe there are many, and the data are uninformative about low amplitude
planets, then the posterior distribution for $N$ will also indicate that there
may be many low amplitude planets. However, their other properties, such as
their orbital periods, will not be well determined.

@@

>>>>

An apparently strange choice is the conditional prior for the (logarithms of)
the orbital
periods, which is a biexponential distribution. A more conventional choice
would have been a normal distribution. However, the \citet{rjobject} software
needs to know the corresponding cumulative distribution and its inverse, which
are not available in closed form for the normal distribution.
The prior for the velocity semi-amplitudes $\{A_i\}$ is important and will affect the
inferred number of planets $N$. For example, if the prior allows for very
low amplitude planets to exist, the data will not rule this out, and the posterior
for $N$ will include the possibility of large numbers of planets. The prior
will influence how many of these low amplitude planets will exist: if we
believe there are many, and the data are uninformative about low amplitude
planets, then the posterior distribution for $N$ will also indicate that there
may be many low amplitude planets. However, their other properties, such as
their orbital periods, will not be well determined. The Beta prior for
eccentricity was suggested by Gregory (priv. comm) and is an approximation
to the inferred frequency distribution of eccentricities in the population
\citep{kipping}.

@@

\bibitem[\protect\citeauthoryear{Kipping}{2013}]{kipping} 
Kipping D.~M., 2013, MNRAS, 434, L51
